Power to the Stimuli: Not the Effect

### 2023-05-17 manuscript_draft.Rmd
updating draft

---
title             : "Power to the Stimuli: Not the Effect"
shorttitle        : "Title"

@@

keywords          : "power, sampling, accuracy in parameter estimation"

>>>>

---
title             : "Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli"
shorttitle        : "Title"

@@

  The planning of the sample size for research studies often focuses on obtaining a significant result given a specified level of power, significance, and an anticipated effect size. This planning requires prior knowledge of the study design and a statistical analysis to calculate the proposed sample size. However, there may not be one specific testable analysis from which to derive power (Silberzahn et al., 2018) or a hypothesis to test for the project (e.g., creation of a stimuli database). Modern power and sample size planning suggestions include accuracy in parameter estimation (AIPE; Maxwell et al., 2008) and simulation of proposed analyses (Chalmers & Adkins, 2020). These toolkits provide flexibility in traditional power analyses that focus on the if-this, then-that approach, yet, both AIPE and simulation require either a specific parameter (e.g., mean, effect size, etc.) or statistical test for planning sample size. In this tutorial, we explore how AIPE and simulation approaches can be combined to accommodate studies that may not have a specific hypothesis test or wish to account for the potential of a multiverse of analyses. Specifically, the examples focus on studies that adopt multiple items and suggest that sample sizes can be planned to measure those items adequately and precisely, regardless of statistical test. We demonstrate that pilot data can be used to determine a sample size that represents well-measured data.  This tutorial also provides multiple code vignettes that researchers can adapt and apply to their own measures.

keywords          : "accuracy in parameter estimation, power, sampling, simulation, hypothesis testing"
